---
title: "Project_V1"
author: "Christine Iyer"
date: "2/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```
```{r fig.height=20, fig.width=9}
library(lubridate)
library(tidyverse)
library(knitr)
library(plotly)
library(tidytext)
library(gridExtra) #viewing multiple plots together
#text mining
library(wordcloud2) #creative visualizations
library(kableExtra)
library(formattable)

```

### [Citicard Complaints](https://data.world/1947theindia/url-httpsdataworld1947theindiadrug-spending/workspace/file?agentid=dataquest&datasetid=bank-and-credit-card-complaints&filename=Credit_Card_Complaints.csv)


```{r}
X <- read.csv("/Users/christineiyer/Downloads/Bank_Account_or_Service_Complaints.csv", header = T, stringsAsFactors = F)
X_1 <- X %>% mutate(Date.received = as.POSIXct(Date.received, format = "%m/%d/%Y"), Date.sent.to.company = as.POSIXct(Date.sent.to.company, format = "%m/%d/%Y"))
tail(X_1)

AnotherX <- read.csv("/Users/christineiyer/Downloads/Credit_Card_Complaints.csv", header = T, stringsAsFactors = F)
AnotherX_1 <- AnotherX %>% mutate(Date.received = as.POSIXct(Date.received, format = "%m/%d/%Y"), Date.sent.to.company = as.POSIXct(Date.sent.to.company, format = "%m/%d/%Y"))
names(AnotherX_1)
```
```{r fig.height=20, fig.width=8}
# ggplot(AnotherX, aes(x = Company,fill = Company)) + geom_bar() + facet_wrap(~Issue, ncol = 3)
```


```{r}
Citi <- AnotherX_1 %>% filter(Company == "Citibank")
```

 
  


```{r fig.height=20, fig.width=9}
Citi_1 <- AnotherX_1 %>% filter(Company == "Citibank") %>% mutate(year = year(Date.received), month = month(Date.received),MonetaryRelief =
                  ifelse(Company.response.to.consumer == "In progress", "In progress",
                         ifelse(Company.response.to.consumer == "Untimely repsponse", "Untimely response",
                                ifelse(Company.response.to.consumer %in% c("Closed with monetary relief", "Closed with relief"), "Monetary Relief", "Non-Monetary Relief")))) %>%
  group_by(year, Issue, MonetaryRelief) %>% summarise(Count = n())
  
  
# ggplot(Citi, aes(x = Company.response.to.consumer,fill = Company.response.to.consumer)) + geom_bar() + facet_wrap(~Issue, ncol = 3)
# head(Citi_1)
# ggplot(Citi_1, aes(x = year, y = Count, group = MonetaryRelief, color = MonetaryRelief)) + 
#   geom_line() + 
#   facet_wrap(~Issue, ncol = 3) 
# ggplotly()
```

```{r fig.height=20, fig.width=9}
# Citi %>% group_by(Date.received, Company.response.to.consumer, Issue) %>% summarise(Count = n()) %>%  ggplot(., aes(x = Date.received, fill = Company.response.to.consumer)) + geom_area(stat = "bin")+ facet_wrap(~Issue, ncol = 3)
```

### Company.response.to.consumer

```{r fig.height=30, fig.width=9}
# plotCiti <- ggplot(Citi, aes(x = Date.received, color = Company.response.to.consumer, fill = Company.response.to.consumer)) + geom_area(stat = "bin")+ facet_wrap(~Issue, ncol = 3)
# ggplotly()
```


### Timely.response.

```{r fig.height=30, fig.width=9}
# plotCiti <- ggplot(Citi, aes(x = Date.received, color = Timely.response., fill = Timely.response.)) + geom_area(stat = "bin")+ facet_wrap(~Issue, ncol = 3)
# ggplotly()
```

### Consumer.disputed.

```{r fig.height=30, fig.width=9}
# plotCiti <- ggplot(Citi, aes(x = Date.received, color = Consumer.disputed., fill = Consumer.disputed.)) + geom_area(stat = "bin")+ facet_wrap(~Issue, ncol = 3)
# ggplotly()
```
```{r fig.height=25, fig.width=9}
# Citi %>% 
#   mutate(MonetaryRelief = 
#                   ifelse(Company.response.to.consumer == "In progress", "In progress", 
#                          ifelse(Company.response.to.consumer == "Untimely repsponse", "Untimely response", 
#                                 ifelse(Company.response.to.consumer %in% c("Closed with monetary relief", "Closed with relief"), "Monetary Relief", "Non-Monetary Relief")))) %>%  
#   group_by(Date.received, Issue, MonetaryRelief) %>% summarise(Count = n()) %>% 
#   ggplot(., aes(x = Date.received, y = Count, group = MonetaryRelief, color = MonetaryRelief)) + 
#   geom_smooth(se = FALSE) + 
#   facet_wrap(~Issue, ncol = 3) 
# ggplotly()
```
### Explore the language sentiments
NRC lexicon matches best


```{r}
# head(Citi)
# unique(Citi$Consumer.complaint.narrative)
```
```{r}
#Customize the text tables for consistency using HTML formatting
my_kable_styling <- function(dat, caption) {
  kable(dat, "html", escape = FALSE, caption = caption) %>%
  kable_styling(bootstrap_options = c("striped", "condensed", "bordered"),
                full_width = FALSE)
}
```



```{r}
#glimpse(prince[139,])
#str(prince[139, ]$Text, nchar.max = 300)
fix.contractions <- function(doc) {
  # "won't" is a special case as it does not expand to "wo not"
  doc <- gsub("won't", "will not", doc)
  doc <- gsub("can't", "can not", doc)
  doc <- gsub("n't", " not", doc)
  doc <- gsub("'ll", " will", doc)
  doc <- gsub("'re", " are", doc)
  doc <- gsub("'ve", " have", doc)
  doc <- gsub("'m", " am", doc)
  doc <- gsub("'d", " would", doc)
  # 's could be 'is' or could be possessive: it has no expansion
  doc <- gsub("'s", "", doc)
  return(doc)
}

# fix (expand) contractions


Citi$Consumer.complaint.narrative <- sapply(Citi$Consumer.complaint.narrative, fix.contractions)
#range(prince$Date)
```

```{r}
Citi <- Citi %>%  mutate(year = year(Date.received), month = month(Date.received)) 
head(Citi)
```


```{r}
# function to remove special characters
removeSpecialChars <- function(x) gsub("[^a-zA-Z0-9 ]", " ", x)
# remove special characters
Citi$Consumer.complaint.narrative <- sapply(Citi$Consumer.complaint.narrative, removeSpecialChars)
# convert everything to lower case
Citi$Consumer.complaint.narrative <- sapply(Citi$Consumer.complaint.narrative, tolower)
#str(prince[19, ]$Text, nchar.max = 300)
#get facts about the full dataset
#summary(prince)
head(Citi)
dim(Citi)
```

```{r}
undesirable_words <- c("Citibank", "Citi")
```
```{r}
data_words_filtered <- Citi %>%
  mutate(index = as.numeric(paste0(year, ".", month))) %>% 
  #breaks lyrics into words and puts them into a new column
  unnest_tokens(word, Consumer.complaint.narrative) %>%
  #takes out the stop words
  anti_join(stop_words) %>%
  #removes duplicate records
  distinct() %>%
  #removes (at the discretion of the analyst) undesirable words that were made into a vector)
  filter(!word %in% undesirable_words) %>%
  #removes words with less than 4 letters
  filter(nchar(word) > 3)
#class(prince_words_filtered)
dim(data_words_filtered)
head(data_words_filtered)
```



```{r}
full_word_count <- data_words_filtered %>% 
  #unnest_tokens(word, Consumer.complaint.narrative) %>% 
  group_by(index, Company.response.to.consumer) %>% 
  summarise(num_words = n()) %>% 
  arrange(desc(num_words))

full_word_count[1:10,] %>% 
  ungroup(num_words, Complaint.ID) %>% 
  mutate(num_words = color_bar("lightyellow")(num_words)) %>% 
  mutate(song = color_tile("lightpink", "lightpink")(Company.response.to.consumer)) %>% 
  kable("html", escape = F, align = "c", caption = "Tickets With Highest Word Count") %>% 
  kable_styling(bootstrap_options = c("striped", "condensed", "bordered"), full_width = F)
```
```{r}
new_sentiments <- sentiments %>% #From the tidytext package
  #filter(lexicon != "loughran") %>% #Remove the finance lexicon
  mutate( sentiment = ifelse(lexicon == "AFINN" & score >= 0, "positive",
                              ifelse(lexicon == "AFINN" & score < 0,
                                     "negative", sentiment))) %>%
  group_by(lexicon) %>%
  mutate(words_in_lexicon = n_distinct(word)) %>%
  ungroup()
data_words_filtered%>%
  mutate(words_in_call = n_distinct(word)) %>%
  inner_join(new_sentiments) %>%
  group_by(lexicon, words_in_call, words_in_lexicon) %>%
  summarise(lex_match_words = n_distinct(word)) %>%
  ungroup() %>%
  mutate(total_match_words = sum(lex_match_words), #Not used but good to have
         match_ratio = lex_match_words / words_in_call) %>%
  select(lexicon, lex_match_words,  words_in_call, match_ratio) %>%
  mutate(lex_match_words = color_bar("lightpink")(lex_match_words),
         lexicon = color_tile("lightgreen", "lightgreen")(lexicon)) %>%
  my_kable_styling(caption = "Lyrics Found In Lexicons")
```


```{r fig.height=100, fig.width=9}
head(data_words_filtered)
jane_austin_sentiment <- data_words_filtered %>% 
  inner_join(get_sentiments("nrc")) %>%
  count(word, index, sentiment, Company.response.to.consumer ) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)

head(jane_austin_sentiment)

head(data_words_filtered)
ggplot(jane_austin_sentiment, aes(index, sentiment, fill = Company.response.to.consumer)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Company.response.to.consumer , ncol = 2, scales = "free_x")
  
```

Find which words are more commonly used in the unhappy consumers narratives and focus on using these types of narratives for cases to consider for intervention.

  

**The three sets of plots above tell a story.**

* Interest Rates
* Billing Disputes
* Billing Statements
* Customer Service
* Delinquent Accounts
* Late Fees
* Fraud Issues



